Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-01-15 ms.rmd
Fixed convergence issue for het freshwater model

We first tested the degree to which acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine ecosystems). Models included an interaction between effect type (i.e., acute or acclimation) and habitat. Reduced mean $lnRR_{Q_{10}}_{acclimation}$ relative to $lnRR_{Q_{10}}_{acute}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10}}_{acute}$ and $lnRR_{Q_{10}}_{acclimation}$ suggests organisms are not capable of physiological plasticity [@Havird2020]. In contrast, a difference in $lnCVR_{Q_{10}}_{acclimation}$ relative to $lnCVR_{Q_{10}}_{acute}$ would imply that changes in between individual variation in physiological rates across 10$^{\circ}$C differ depending on whether acute or acclimation responses are measured. If the interaction between effect type and habitat was not supported, then we fit a model that only contained additive effects of effect type and habitat. Following on from these models, we subset each habitat type and explored how mean $lnRR_{Q_{10}}$ changed across traits. Within each habitat (marine, freshwater, and terrestrial) we fit a series of models that included an interaction between effect type (acute / acclimation) and trait category (as defined above). Variance in effects within trait categories appeared to vary depending on the trait type in question. Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = ,  and terrestrial = )

@@

  # Heteroscedastic variance model for freshwater
  model1.3_f_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 + trait_category | obs),
                              R = list(species_full =f_phylo), struct = "HCS", rho = 0, dfs = "contain", 
                              test = "t", data = lnRRQ10_data_f)

  ## Check support for two models
  AIC(model1.3_f_het, model1.3_f)

  # Run the Bayesian equivalent of the top supported model. 
   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)

>>>>

We first tested the degree to which acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine ecosystems). Models included an interaction between effect type (i.e., acute or acclimation) and habitat. Reduced mean $lnRR_{Q_{10}}_{acclimation}$ relative to $lnRR_{Q_{10}}_{acute}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10}}_{acute}$ and $lnRR_{Q_{10}}_{acclimation}$ suggests organisms are not capable of physiological plasticity [@Havird2020]. In contrast, a difference in $lnCVR_{Q_{10}}_{acclimation}$ relative to $lnCVR_{Q_{10}}_{acute}$ would imply that changes in between individual variation in physiological rates across 10$^{\circ}$C differ depending on whether acute or acclimation responses are measured. If the interaction between effect type and habitat was not supported, then we fit a model that only contained additive effects of effect type and habitat. Following on from these models, we subset each habitat type and explored how mean $lnRR_{Q_{10}}$ changed across traits. Within each habitat (marine, freshwater, and terrestrial) we fit a series of models that included an interaction between effect type (acute / acclimation) and trait category (as defined above). Variance in effects within trait categories appeared to vary depending on the trait type in question. Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = 120, and terrestrial = )

@@

  # Heteroscedastic variance model for freshwater
  model1.3_f_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 + trait_category | obs),
                              R = list(species_full =f_phylo), struct = "HCS", rho = 0, dfs = "contain", 
                              test = "t", data = lnRRQ10_data_f, method = "REML", control=list(iter.max=1000, rel.tol=1e-8))

  ## Check support for two models
  AICc_model1.3_f_het <- AIC(model1.3_f_het) + AICc_correction(model1.3_f_het). # Clearly better supported.
      AICc_model1.3_f <- AIC(model1.3_f) + AICc_correction(model1.3_f)
  delat_AICc_model1.3_f <- AICc_model1.3_f - AICc_model1.3_f_het

  # Run the Bayesian equivalent of the top supported model. 
   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait) + (1+trait_category|gr(obs, cor = FALSE)), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)
